The Role of Variability in Learning Generalization: A Computational Modeling Approach

### 2024-05-18 Presentation/slides.qmd
Add embeded view of slides; re-render major pages.

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
subtitle: "Dissertation Defense"
format: 
  html: default
  clean-revealjs:
    #theme: moon #white
    output-ext: slide.html
    slideNumber: true
    center: true
    chalkboard: true
  pptx:
    incremental: true
author:
  - name: Thomas Gorman
    orcid: 0000-0000-0000-0000
    affiliations: Indiana University
---

>>>>

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
subtitle: "Dissertation Defense"
format: 
  html: default
  clean-revealjs:
    #theme: moon #white
    #output-ext: revealjs.html
    output-file: slides_revealjs
    slideNumber: true
    center: true
    chalkboard: true
  pptx:
    incremental: true
author:
  - name: Thomas Gorman
    orcid: 0000-0000-0000-0000
    affiliations: Indiana University
---

::: {.content-visible when-format="html" unless-format="revealjs"}

<div class="ratio ratio-16x9"> <iframe src="/Presentation/slides_revealjs.html"></iframe> </div>

:::
